\TheTitle

### 2016-04-22 linvis.tex
Another run at the introduction
Editing the introduction again.

\newif\ifdraft
% \drafttrue

@@

Maintainers of older versions of the Linux kernel must sift through thousands of
commits with tools that are unable to filter and effectively visualize projects at
the scale of the kernel. Tools like Gitk use the DAG model, showing all commits and
merges in chronological order to when the commit was authored. This representation
works in smaller projects, enabling users to see when changes are made, when these
changes are merged, and how each branch is interacting. In large modular projects,
like the Linux kernel, the DAG becomes a mess of merges and commits (figure
\ref{fig:gitk}), losing its visual meaning. In some cases, the Linux kernel is
simply too large for the system to generate a visualization. Github provides a DAG
view for many projects, but is unable to display the visualization for projects as
large as the Linux kernel (figure \ref{fig:gitfail}).

@@

Git cannot store the date that a commit was merged into a branch due to the rebase
operation.  When a rebase occurs, several changes could be made to the commit. It
may be squashed with other commits, combining the effects of several commits into a
single commit. It may be dropped altogether, in which case the commit is no-longer
merged.  It may be that the entire branch has simply been re-rooted to another
position on the DAG. Due to this, tools are unable to determine when a commit is
merged. A user may decide that it is important to be able to see only the commits
contributing to a given release, that is commits that were merged with the
Linus-branch of the kernel between two given dates. This operation is not possible
without the collection of additional data that is not provided by git. Git only
enables users to see when commit was authored, not when it was merged into a branch.

@@

In this paper, we present our design decisions behind a web-based
tool\footnote{\url{http://li.turingmachine.org}} built around a tree-based model
instead of a DAG. Our tool provides information about the location of a given commit
in the respective merge tree, the files edited, the modules edited, and the commit
message for a given commit or merge. The tool allows users to apply various filters,
including the release version, along with a keyword or phrase from the log preview,
the name of the author, or the commit id. The user can request all the root-level
merges containing a commit or merge that matches the query, or all commits and
merges that match the query.

@@

Our core model provides advantages to the DAG model used by other tools. By
separating and focusing on sub-trees from the whole repository, we are able to
filter out commits and merges that do not pertain to a component of the kernel. This
provides a clearer picture of what is happening in a given merge. The second benefit
to the tree model is that it enables us to automatically aggregate metadata.

In addition to this, the model provides us with a mechanism of performing date-range
queries with meaningful results. Using the tree built by a continuous mining system
enables us a mechanism to perform date-range queries with meaningful results.

>>>>

\newif\ifdraft
\drafttrue

@@

Maintainers of older versions of the Linux kernel must sift through thousands of
commits with tools that are unable to filter and effectively visualize projects at
the scale of the kernel. Tools like Gitk use a directed acyclic graph (DAG) model,
showing all commits and merges in chronological order by when the commit was
authored. This representation works in smaller projects; it enables users to see
when changes are made, when these changes are merged, and how each branch is
interacting.  In large modular projects, like the Linux kernel, the DAG becomes a
mess of merges and commits (figure \ref{fig:gitk}) losing its visual meaning. In
some cases, the Linux kernel is simply too large for the system to generate a
visualization. Github provides a DAG view for many projects, but is unable to
display the visualization for projects as large as the Linux kernel (figure
\ref{fig:gitfail}).

@@

Git cannot store the date that a commit was merged into a branch due to the rebase
operation. A rebase can perform serveral changes to commits and merges. It may be
squashed with other commits, combining the effects of several commits into a single
commit. It may be dropped altogether, in which case the commit is no-longer merged.
It may be that the entire branch has simply been re-rooted to another position on
the DAG. Due to this, tools are unable to determine when a commit is merged. A user
may decide that it is important to be able to see only the commits contributing to a
given release, that is commits that were merged with the Linus-branch of the kernel
between two given dates. This operation is not possible without the collection of
additional data that is not provided by git. Git only enables users to see when a
commit was authored, not when it was merged into a branch.

@@

In this paper, we present our design decisions behind a web-based
tool\footnote{\url{http://li.turingmachine.org}} built around the tree-based model
instead of a DAG. Our tool provides information about the location of a given commit
in the respective merge tree, the files edited, the modules edited, and the commit
message for a given commit or merge. The tool allows users to apply various filters,
including the release version, along with a keyword or phrase from the log preview,
the name of the author, or the commit id. The user can request all the root-level
merges containing a commit or merge that matches the query, or all commits and
merges that match the query.

@@

Our core model provides advantages to the DAG model used by other tools. We separate
the commits and merges into sub-trees and focus on a single sub-tree at a time. This
enables us to filter out commits and merges that do not pertain to the component of
the kernel that we are interested in, providing a clearer picture of what is
happening in a given merge. The tree model also enables us to aggregate metadata
easily. With the addition of the continuous polling of the repository, the model
provides us with a mechanism of performing date-range queries with meaningful
results.
